### 2020-09-24 Thesis-Chapter3-Arguments.tex
Work on DFDs

@@

- Easy answers
- Fallacies!

@@

Note: a problem with muddling through wicked problems is that each attempted fix leads to long lasting unintended side
effects. This is especially true with matters of encryption, where the data could be stored for years till it can be
decrypted! So must be very careful to avoid solution attempts that leave long scars.

>>>>

Wicked problems

@@

- Easy answers
  - EA mandates, complexity denial
- Fallacies!
- Bad results with long technical tails

% Note: a problem with muddling through wicked problems is that each attempted fix leads to long lasting unintended side
% effects. This is especially true with matters of encryption, where the data could be stored for years till it can be
% decrypted! So must be very careful to avoid solution attempts that leave long scars.

@@
